---
title: "Analyses for 'Spoken Word Processing in Bilingual Older Adults: Assessing Within- and Cross-Language Competition using the Visual World Task'" 
output:
 html_document:
  df_print: paged
 word_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=120)

library(data.table)
library(lme4)
library(lmerTest)
library(effects)
library(ggplot2)

#devtools::install_github("crsh/papaja")
library(papaja)
```

# Load and prepare data
```{r echo=TRUE}
# First window
data_200_600 <- read.csv("data/data_200_600.csv",header=TRUE, encoding="UTF-8")

# Second window
data_600_1000 <- read.csv("data/data_600_1000.csv",header=TRUE, encoding="UTF-8")

# Mouse click data
data_200_1000 <- read.csv("data/data_200_1000.csv",header=TRUE, encoding="UTF-8")

# Factoring relevant variables
data_200_600$word_heard <- factor(data_200_600$word_heard)
data_600_1000$word_heard <- factor(data_600_1000$word_heard)
data_200_1000$word_heard <- factor(data_200_1000$word_heard)

data_200_600$displayR <- factor(data_200_600$displayR)
data_600_1000$displayR <- factor(data_600_1000$displayR)
data_200_1000$displayR <- factor(data_200_1000$displayR)

data_200_600$Group_Age  <- factor(data_200_600$Group_Age)
data_600_1000$Group_Age <- factor(data_600_1000$Group_Age)
data_200_1000$Group_Age <- factor(data_200_1000$Group_Age)

# Deviation coding relevant variables
contrasts(data_200_600$word_heard) <- -1 * contr.sum(2)/2
contrasts(data_600_1000$word_heard) <- -1 * contr.sum(2)/2
contrasts(data_200_1000$word_heard) <- -1 * contr.sum(2)/2

contrasts(data_200_600$Group_Age)  <- -1 * contr.sum(2)/2
contrasts(data_600_1000$Group_Age) <- -1 * contr.sum(2)/2
contrasts(data_200_1000$Group_Age) <- -1 * contr.sum(2)/2

# Note: deviation coding for display factor is done in the model call, since it's a multi-level factor
```


# Within-language competition

## Fixations to target pictures as a function of display (competitor display vs. no-competitor display), only when the target was heard 

### 200 - 600
```{r}
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1 + displayR | Participant) + (1 + displayR + Group_Age | set), 
           data = data_200_600[data_200_600$word_heard == "T" & data_200_600$displayR != "zFD" & 
                               data_200_600$displayR != "zEFD",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)

# Older alone
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1 + displayR | Participant) + (1 | set), 
           data = data_200_600[data_200_600$word_heard == "T" & data_200_600$displayR != "zFD" & 
                               data_200_600$displayR != "zEFD" & data_200_600$Group_Age=="zO",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)

# Younger alone
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1  | Participant) + (1 | set), 
           data = data_200_600[data_200_600$word_heard == "T" & data_200_600$displayR != "zFD" & 
                               data_200_600$displayR != "zEFD" & data_200_600$Group_Age=="Y",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)


```

### 600 - 1000
```{r}
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 + displayR + Group_Age | set), 
           data = data_600_1000[data_600_1000$word_heard == "T" & data_600_1000$displayR != "zFD" &
                                data_600_1000$displayR != "zEFD",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)

# Older alone
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 + displayR | set), 
           data = data_600_1000[data_600_1000$word_heard == "T" & data_600_1000$displayR != "zFD" &
                                data_600_1000$displayR != "zEFD" & data_600_1000$Group_Age == "zO",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)

# Younger alone
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 + displayR | set), 
           data = data_600_1000[data_600_1000$word_heard == "T" & data_600_1000$displayR != "zFD" &
                                data_600_1000$displayR != "zEFD" & data_600_1000$Group_Age == "Y",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)


```

## Fixations to within-language competitor pictures as a function of word heard (target vs. control), only when competitor displays were presented

### 200 - 600
```{r}
mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 + word_heard + Group_Age | set), 
           data = data_200_600[data_200_600$displayR == "zED",])

summary(mod)


mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) + TRIAL_LABEL +  WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 + word_heard | set), 
           data = data_200_600[data_200_600$displayR == "zED" & data_200_600$Group_Age == "zO",])

summary(mod)


mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 + word_heard | set), 
           data = data_200_600[data_200_600$displayR == "zED" & data_200_600$Group_Age == "Y",])

summary(mod)
```

### 600 - 1000
```{r}
mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 + Group_Age | set), 
           data = data_600_1000[data_600_1000$displayR == "zED"  ,])

summary(mod)

figure3.mod <- mod

mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 | set), 
           data = data_600_1000[data_600_1000$displayR == "zED"  & data_600_1000$Group_Age == "zO" ,])

summary(mod)

mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 | set), 
           data = data_600_1000[data_600_1000$displayR == "zED"  & data_600_1000$Group_Age == "Y" ,])

summary(mod)
```


### Plot Figure 3
```{r}
ef <- data.frame(Effect(c("Group_Age", "word_heard", "prop_phondiv_T_ED"), 
                        figure3.mod, confidence.level = .6827,
                        fixed.predictors = list(given.values = c(WASI.Vocab.Scaled.Score = 13.56, 
                                                                 TRIAL_LABEL = 85))))
                        # median trial and mean wasi score of the sample

group_age_names <- c(
  "Y"  = "Younger adults",
  "zO" = "Older adults"
)

ggplot(ef, aes(x = prop_phondiv_T_ED, y = fit, group = word_heard, linetype = word_heard, 
               ymin = lower, ymax = upper)) + 
  geom_line() + geom_ribbon(alpha = .2) + 
  facet_wrap( ~ Group_Age, labeller = as_labeller(group_age_names)) + 
  coord_cartesian(ylim = c(0,.3)) +
  labs(x = "Proportion phonological overlap",
       y = "Model-predicted\nfixation proportion to competitor",
       linetype = "Word heard") +
  scale_linetype(labels = c("Control", "Target")) +
  theme_apa(base_size = 14)
ggsave("figures/figure_3.png", width = 15, height = 9, units = "cm")
```

## Correct mouse clicks for within-language competitor-display trials as a function of word heard (target vs. control)
```{r}
mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_ED) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1 | Participant) +   (1 | set), 
           data = data_200_1000[data_200_1000$displayR == "zED",])

summary(mod)

mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1 | Participant) +   (1 | set), 
           data = data_200_1000[data_200_1000$displayR == "zED" & data_200_1000$Group_Age == "zO",])

summary(mod)

mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_ED) + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1 | Participant) +   (1 | set), 
           data = data_200_1000[data_200_1000$displayR == "zED" & data_200_1000$Group_Age == "Y",])

summary(mod)
```

## Interactions with English-language proficiency for older adults alone 
```{r}
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL +
             WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1|set), 
           data = data_200_600[data_200_600$word_heard == "T" & data_200_600$displayR != "zFD" & 
                               data_200_600$displayR != "zEFD" & data_200_600$Group_Age == "zO",],
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)

mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_ED) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL +
             WASI.Vocab.Scaled.Score + 
             (1|Participant) + (1|set), 
           data = data_600_1000[data_600_1000$word_heard == "T" & data_600_1000$displayR != "zFD" &
                                data_600_1000$displayR != "zEFD" & data_600_1000$Group_Age == "zO",],
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)

#

mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) * scale(RT_Ratio_En_Fr_Liv_NonLiv) +
             TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 | set), 
           data = data_200_600[data_200_600$displayR == "zED" & data_200_600$Group_Age == "zO"  ,])

summary(mod)

mod = lmer(Eng_Comp.prop ~ word_heard * scale(prop_phondiv_T_ED) * scale(RT_Ratio_En_Fr_Liv_NonLiv) +
            TRIAL_LABEL +  WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 | set), 
           data = data_600_1000[data_600_1000$displayR == "zED" & data_600_1000$Group_Age == "zO"  ,],)

summary(mod)

#

mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_ED) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL +
             WASI.Vocab.Scaled.Score + 
             (1 | Participant) + (1 | set), 
           data = data_200_1000[data_200_1000$displayR == "zED" & data_200_1000$Group_Age == "zO" ,])

summary(mod)
```

# Cross-language competition

## Fixations to target pictures as a function of display (competitor display vs. no-competitor display), only when the target was heard

### 200 - 600
```{r}
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_FD) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1  |Participant) + (1 + displayR + Group_Age |set), 
           data = data_200_600[data_200_600$word_heard == "T" & data_200_600$displayR != "zED" & 
                                 data_200_600$displayR != "zEFD",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)
```

### 600 - 1000
```{r}
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_FD) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score +
             (1 |Participant) + (1 + displayR + Group_Age |set), 
           data = data_600_1000[data_600_1000$word_heard == "T" & data_600_1000$displayR != "zED" &
                                  data_600_1000$displayR != "zEFD",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)
```

## Fixations to cross-language competitor pictures as a function of word heard (target vs. control), only when competitor displays were presented

### 200 - 600
```{r}
mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1 + word_heard + Group_Age |set), 
           data = data_200_600[data_200_600$displayR == "zFD",])

summary(mod)

mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1  |set), 
           data = data_200_600[data_200_600$displayR == "zFD" & data_200_600$Group_Age == "zO",],)

summary(mod)

mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1 + word_heard |set), 
           data = data_200_600[data_200_600$displayR == "zFD" & data_200_600$Group_Age == "Y",],)

summary(mod)
```

### 600 - 1000
```{r}
mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 + word_heard |Participant) + (1 + word_heard + Group_Age |set), 
           data = data_600_1000[data_600_1000$displayR == "zFD",],)

summary(mod)

figure5.mod <- mod

mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 + word_heard |Participant) + (1 + word_heard |set), 
           data = data_600_1000[data_600_1000$displayR == "zFD" & data_600_1000$Group_Age == "zO",],)

summary(mod)

mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 + word_heard |Participant) + (1 + word_heard |set), 
           data = data_600_1000[data_600_1000$displayR == "zFD" & data_600_1000$Group_Age == "Y",],)

summary(mod)
```

### Plot Figure 5
```{r}
ef <- data.frame(Effect(c("Group_Age", "word_heard", "prop_phondiv_T_FD"), 
                        figure5.mod, confidence.level = .6827,
                        fixed.predictors=list(given.values = c(WASI.Vocab.Scaled.Score = 13.56, TRIAL_LABEL = 85))))
                        # median trial and mean wasi score of the sample

group_age_names <- c(
  "Y"  = "Younger adults",
  "zO" = "Older adults"
)

ggplot(ef, aes(x = prop_phondiv_T_FD, y = fit, group = word_heard, 
               linetype = word_heard, ymin = lower, ymax = upper)) + 
  geom_line() + geom_ribbon(alpha = .2) + 
  facet_wrap(~ Group_Age, labeller = as_labeller(group_age_names)) + 
  coord_cartesian(ylim = c(0, .3)) +
  labs(x = "Proportion phonological overlap",
       y = "Model-predicted\nfixation proportion to competitor",
       linetype = "Word heard") +
  scale_linetype(labels=c("Control", "Target")) +
  theme_apa(base_size = 14)
ggsave("figures/figure_5.png", width = 15, height = 9, units = "cm")
```

## Correct mouse clicks for cross-language competitor-display trials as a function of word heard (target vs. control) 
```{r}
mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_FD) * Group_Age + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 + word_heard |Participant) + (1 + word_heard + Group_Age | set), 
           data = data_200_1000[data_200_1000$displayR == "zFD",],)

summary(mod)

mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_FD) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 + word_heard |Participant) + (1 + word_heard |set), 
           data = data_200_1000[data_200_1000$displayR == "zFD" & data_200_1000$Group_Age == "zO",],)

summary(mod)

mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_FD) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 + word_heard |Participant) + (1 + word_heard |set), 
           data = data_200_1000[data_200_1000$displayR == "zFD" & data_200_1000$Group_Age == "Y",],)

summary(mod)
```

## Interaction with English-language proficiency in older adults 
```{r}
# 
mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_FD) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL +
             WASI.Vocab.Scaled.Score + 
             (1  |Participant) + (1 |set), 
           data = data_200_600[data_200_600$Group_Age =="zO" & data_200_600$word_heard == "T" & 
                                 data_200_600$displayR != "zED" & data_200_600$displayR != "zEFD",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)

mod = lmer(Target.prop ~ displayR * scale(prop_phondiv_T_FD) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL +
             WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1 | set), 
           data = data_600_1000[data_600_1000$Group_Age =="zO" & data_600_1000$word_heard == "T" & 
                                  data_600_1000$displayR != "zED" & data_600_1000$displayR != "zEFD",], 
           contrasts = list(displayR = -1*contr.sum(2)/2))

summary(mod)


# 
mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL +WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1 |set), 
           data = data_200_600[data_200_600$Group_Age =="zO" & data_200_600$displayR == "zFD"  ,],)

summary(mod)

mod = lmer(Fr_Comp.prop ~ word_heard * scale(prop_phondiv_T_FD) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL + WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1 |set), 
           data = data_600_1000[data_600_1000$Group_Age =="zO" & data_600_1000$displayR == "zFD"  ,],)

summary(mod)

# 
mod = lmer(Click.RT ~ word_heard * scale(prop_phondiv_T_FD) * scale(RT_Ratio_En_Fr_Liv_NonLiv) + TRIAL_LABEL +
             WASI.Vocab.Scaled.Score + 
             (1 |Participant) + (1 |set), 
           data = data_200_1000[data_200_1000$Group_Age == "zO" & data_200_1000$displayR == "zFD"  ,],)

summary(mod)
```